%! TeX program = xelatex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Mark}{Lucernas}{
\href{mailto:lucernas.mj@gmail.com}{lucernas.mj@gmail.com} | 858.371.8649 \\
\href{https://github.com/marklcrns}{\bf github.com/marklcrns} | \href{https://www.linkedin.com/in/marklucernas}{\bf linkedin.com/in/marklucernas}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.60\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Personal Projects}

\runsubsection{Generals-2.0}
\descript{| \textbf{\href{https://github.com/marklcrns/Generals-2.0}{GITHUB}}}
\location{Sept 2020 – Present}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item \textbf{\href{https://libgdx.badlogicgames.com/}{libGDX}} rewrite of my first iteration \textbf{\href{https://github.com/marklcrns/java-game-of-generals}{java-game-of-generals}}.
\item A 9x8 strategy board game aiming for a cross-platform support as well as competitive AI implementation.
\item Single player gameplay powered by Minimax Algorithm, as well as online gaming (in progress) through Socket Programming.
\end{tightemize}

\runsubsection{Website Project}
\descript{| \textbf{\href{https://github.com/marklcrns/CS50-Week5-Website-Project}{GITHUB}}}
\location{Nov 2019}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Basic website created to solidify my understanding of HTML, CSS, and JavaScript, and also for an online course project submission.
\item Fundamental usage of Bootstrap library with CSS Grid layout approach that handles dynamic screen resizing.
\end{tightemize}

\runsubsection{Bash Scripts}
\descript{| \textbf{\href{https://github.com/marklcrns/scripts}{GITHUB}}}
\location{Sept 2020 - Oct 2020}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item \textbf{\href{https://github.com/marklcrns/scripts/tree/master/tools/dotfiles}{Dotfiles Manager}} and \textbf{\href{https://github.com/marklcrns/scripts/tree/master/tools/git}{Local Github Repositories Manager}} bash utility scripts.
\item Helps backing up/distribution of .dotfiles as well as simultaneous Github secure commands execution throughout multiple local repositories.
\end{tightemize}

\section{Group Projects}
\runsubsection{The Wizard}
\descript{| \textbf{\href{https://github.com/MiramarCISC/CISC191-SUM20-A}{GITHUB}}}
\location{June 2019 – Aug 2019 | SDCCD | Miramar College }
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Test-driven top-down shooter game.
\item Developed the GUI of the game as well as unit testing via JUnit 5.
\item Designed project architecture.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     WORK EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Work Experience}

\runsubsection{U.S. Navy}
\descript{| Seaman Recruit, E3 }
\location{2018 - 2019 | Great Lakes, IL}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Advanced Electronics Computer Field bootcamp recruit.
\item Leadership position as a Dental Yeoman.
\item Top 2 Division in the whole training group.
\end{tightemize}
{\footnotesize \textit{\textbf{( Veteran, Medically discharged ) }}}
\sectionsep

\runsubsection{IPS Group Inc.}
\descript{| Parking Meter Assembler/Technician }
\location{2017 – 2018 | San Diego, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Assembles parking meters from scratch
\item Troubleshoot and update old parking meter models and replace dysfunctional electrical parts.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}
\subsection{SDCCD}
\descript{Undergraduate Computer Science Major}
\location{2019 - Present | San Diego, CA}
transfering to UCSD \\
\location{Cum. GPA: 3.9 / 4.0}
\location{Honors: Dean's Lister 2015 - 2016}
\sectionsep

\subsection{Self-Education}
\descript{Udemy | edX | MOOC}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Undergraduate}
ARM Assembly \\
Data Structures and Algorithms \\
Introduction and intermediate Java \\
Introduction to C++ \\
Unix and Software Tools, and Scripting \\
Public Speaking
\sectionsep

\subsection{Self-education}
edX - Harvard CS50's Introduction to Computer Science \\
Udemy - Introduction Artificial Neural Network and Deep Learning \\
Udemy - Python for Data Science and Machine Learning Bootcamp \\
Udemy - Linux Shell Scripting \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Technical Skills}
\location{Proficient:}
Java \textbullet{} Python \textbullet{} Bash \textbullet{} JavaScript
\textbullet{} HTML \textbullet{} CSS \textbullet{} VimScript
\textbullet{} Advanced Excel \textbullet{} Linux \textbullet{} Vim/Neovim \\
\location{Familiar:}
C \textbullet{} C++ \textbullet{} MySQL \textbullet{} ARM Assembly \textbullet{}
Lua \textbullet{} Raspberry Pi
\sectionsep

\subsection{Soft Skills}
\location{Outstanding:}
Bilingual Communicator (Filipino, English) \textbullet{} Discipline
\textbullet{} Teamwork \textbullet{} Interpersonal Skills \textbullet{}
Leadership

\end{minipage}
\end{document}  \documentclass[]{article}
